Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-06 doc/JFLA2022/paper.tex

\subsection{Continuous integration and deployment, opam packaging, etc.}
\section{Conclusion and perspectives}

>>>>

\subsection{Technologies supporting the monorepo structure}

Monorepos (shorthand for monolithic repositories) are single repositories containing multiple independent or related packages.
%
They have gained increasing popularity following experiences in large companies such as Google, but are also used at a lesser scale for managing open source projects.
%
They are known to simplify the management of dependencies, making cross-packages changes and refactorings~\cite{brito2018monorepos}.

In the context of Coq projects, they did not use to be well-supported.
%
One of the only monorepo in the Coq ecosystem was the math-comp repository, and it used a custom build infrastructure to make this possible.
%
However, recent improvements in tooling have made their use possible, and therefore we have used them more and more, for instance within \community.

In the context of \Hydras, we rely on the following tools.

\paragraph{The Dune build system}
It allows building packages contained in a single source tree separately, which is essential to be able to publish the different libraries contained in a single repository as separate (opam) packages to the Coq package index.

In practice, we do still support building the whole project with coq\_makefile, and we actually rely on this build system in our documentation generation pipeline.

\paragraph{The Coq Nix Toolbox~\cite{cohen:hal-03366644}}
We rely on this toolbox mainly because it can generate a Continuous Integration setup (relying on GitHub Actions) to test the various libraries contained in the project, but also their dependencies.
%
This has allowed us, for instance, to test the Goedel library with the current version of the Hydra-battles library when we have moved a subpart of Goedel to Hydra-battles (the Ackermann sub-library).

The build artifacts are stored in the \community binary cache on Cachix~\cite{cachix}.
%
This means that a given version never has to be built twice and Continuous Integration can be almost instantaneous when no change has been made (e.g., after merging a pull request).

\section{Conclusion and perspectives}
